Accelerated Inference for Partially Observed Stochastic Processes with Automatic Differentiation

### 2023-12-11 mop/draft.tex
Updates from Overleaf

@@

>>>>

\kevin{Do groups of ten and take the best one from each group. Omit old IF2 from figure in the paper, provide complete figure with old IF2 in the appendix, saying that we modified the settings because of more modern practice. }

\kevin{IFAD beats IF2 x percent of the time on 100 paired runs, but the bigger thing is that it gets close to the MLE without much effort. Previously, we'd have to do many searches, plus refinement (which is necessary, as we can see from the IF2 boxplot, it is easy to fool yourself into thinking that because you see the plateau that is the MLE). This includes likelihood profiling diagnostics, which are very computationally intensive. Now we can just take the best of ten searches -- IFAD does the refinement.}

@@

\kevin{Have an outsider read the manuscript afterwards.}
